\TheTitle

### 2017-07-14 paper/relatedwork.tex
editing related work and adding code swarm

Version control systems monitor the development lifetime of software
projects. This makes the version control system vital in providing
information about how a software project is being developed. To do this,
the user must be able to gain a clear understanding of how commits are
being integrated into the project, along with understanding what changes
these commits are bringing with them. These are the tasks that we set
out to solve with the \mt model. Ideally, we could compare our model
against another that is designed with these goals. To our knowledge, we
know of no git repository visualzation tool that has these specific
goals. This may be due to issues with finding the master branch of the
repository which is a non-trivial task, or due to other factors.

While we have found no tool with the express goal of showing how a
commit is integrated, and providing a summarization of a merge, there
has been a lot of work done in providing visualizations of various
aspects of a repository.

@@

Gource is a tool for providing an interactive timelapse of the state of
a repository\cite{Caudwell2010}. In the timelapse, it shows who
contributes and what type of contribution a developer is making. These
contribution types are one of, adding a file, removing a file, and
changing a file. While the timelapse is interesting to watch, it does
not provide any additional explanation of the changes actually being
made, only the frequency that they are being made and who is making
them.

% TODO: add code_swamp or something like that

% TODO: Check this -- Look into source tree
Git itself is shipped with summarization and visualization tools:
the \verb|git log| command and Gitk, which is a graphical tool for the purpose of browsing
the DAG of the repository.
Many other tools are designed with a similar visual metaphore
as what is presented in Gitk, including Git kraken, Github Desktop and
web interfaces, the Git Lab web intereface, the Bitbucket web interface,
and many others. The Gitk interface is built around the central DAG
viewer. The DAG displays the repository events on their respective
branches, the author, and the date that the event was authored. A user
can select an event to view addition information about it, including the
full commit log, the parents and children of the event, and the diff
generated if modifications were made. In the case of the Linux kernel,
merges are not resolved as merge conflicts in the master repository, but
by the developers prior to merging. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the
commits persist, but Gitk is unable to provide an aggregated view of the
files modified, the patches for those files, and the authors who
contributed commits to that merge.

>>>>

Version control systems monitor the development lifetime of software
projects. This makes the version control system vital in providing
information about how a software project is being developed. To do this,
the user must be able to gain a clear understanding of how commits are
being integrated into the project, along with understanding what changes
these commits are bringing with them. These are the tasks that we set
out to solve with the \mt model. Ideally, we could compare our model
against another that is designed with these goals. To our knowledge, we
know of no git repository visualization tool that has these specific
goals. This may be due to issues with finding the master branch of the
repository which is a non-trivial task, or due to other factors. While
we have found no tool with the express goal of showing how a commit is
integrated, and providing a summarization of a merge, there has been a
lot of work done in providing visualizations of various aspects of a
repository.

@@

Gource is a tool for providing an interactive timelapse of the state of
a repository\cite{Caudwell2010}. In the timelapse, it shows who
contributes and what type of contribution a developer is making. These
contribution types are one of, adding a file, removing a file, and
changing a file. While the timelapse is interesting to watch, it does
not provide any additional explanation of the changes actually being
made, only the frequency that they are being made and who is making
them. Codeswarm\cite{ogawa09} is similar to Gource, using an organic approach to
visualizing events in the repository. Unlike Gource, which focuses on
the files, Codeswarm focuses on developers and the number of commits
they are making.

Git itself is shipped with summarization and visualization tools: the
\verb|git log| command and Gitk, which is a graphical tool for the
purpose of browsing the DAG of the repository. Many other tools are
designed with a similar visual metaphore as what is presented in Gitk,
including GitKraken, Github Desktop and web interfaces, the Git Lab web
interface, the Bitbucket web interface, are a few examples. The Gitk
interface is built around the central DAG viewer. The DAG displays the
repository events on their respective branches, the author, and the date
that the event was authored. A user can select an event to view addition
information about it, including the full commit log, the parents and
children of the event, and the diff generated if modifications were
made. In the case of the Linux kernel, merges are not resolved as merge
conflicts in the master repository, but by the developers prior to
merging through rebase operations. With this development model, no
merges will have modified any files, and will not show a diff. While the
merge does not make changes directly, the effects of merging the commits
persist, but Gitk is unable to provide an aggregated view of the files
modified, the patches for those files, and the authors who contributed
commits to that merge.
